An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
proof sketch for calibrated

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e. $u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e. $\psi(u) \in \gamma(p)$).
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
\end{proof}

@@

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
The idea will be to map points in $U$, as well as nearby  to something in $R_U$
%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ embedding some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}

@@

\begin{theorem}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then there is link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{theorem}
\raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
\raft{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  [[Is this true?]]}

@@

When embedding, we consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
\end{align*}
and claim that $L_2$ embeds $\ell_2$.

Finally, taking $k = 1$, we see that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$, while the expected loss for $\ell_{top-k}$ is strictly less when predicting $\argmax_y p_y$.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
%		&\leq \frac{k+1}{2k} \\
%		&\leq 1
	\end{align*}
	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?  Another question-- is the risk polyhedral?}

@@

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
%\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}

>>>>

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e. $u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e. $\psi(u) \in \gamma(p)$).
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  \bo{Have we defined trim already? Or is this proof going to the appendix?}
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
\end{proof}

@@

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
The idea will be to map points in $U$, as well as points nearby, to something in $R_U$
%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}

@@

\begin{theorem}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
\end{theorem}

\begin{proof}[Sketch]
  \emph{Well-defined:} Recall that Proposition \ref{prop:embed-link} shows that we can always consistently map each point of $U$ to some member of $R_U$.
  The key point was that if some collection such as $U,U',U''$ overlap at a $u$, then their report sets $R_U, R_{U'}, R_{U''}$ also overlap, so there is a valid choice $r = \psi(u)$.
  Now, we thicken all sets $U \in \U$ by a small enough $\epsilon$ and show that if the \emph{thickened} sets overlap at $u$, then $U,U',U''$ themselves overlap, so again $R_U, R_{U'}, R_{U''}$ overlap and there is a valid chioce $r = \psi(u)$.

  \emph{Calibrated:} By construction of the thickened link, if $u$ maps to a wrong report, i.e. $\psi(u) \not\in \gamma(p)$, then $u$ must have at least distance $\epsilon$ to the optimal set $U = \Gamma(p)$.
  We then show that the minimal gradient of the expected loss along any direction away from $U$ is lower-bounded, giving a constant excess expected loss at $u$.
\end{proof}

\raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
\raft{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  [[Is this true?]]}

@@

When embedding, we consider the discrete loss
\begin{align*}
\ell_2(r,y) &= \Ind[y \not\in r] + \min\left(\frac{|r \setminus \{y\}|}{k}, 1\right)~,~
\end{align*}
and claim that $L_2$ embeds $\ell_2$.  
(3.) Finally, taking $k = 1$, we see that $0 \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) + 0 \\
		&\leq \frac{k+1}{2k} \\
		&\leq 1
	\end{align*}
	\jessie{TODO-- brain is fried and giving up for the night.}

@@

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\cite{pires2013cost}, they typically work in $n$ dimensions.
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}
